---
title: "Test Code"
author: "Chinyere Brown"
date: "12/3/2019"
output: html_document
---

```{r setup, eval=TRUE, echo=TRUE}
library(tidyverse)
library(ggplot2)
library(lubridate)
```

filepath/web address of data. specify data type if not zip. various data manipulation options (reshape and join data, rename/create variables, )  
  
### Websites  
Mecklenburg County:
https://www.mecknc.gov/BOE/data/Pages/VoterDataFileDetails.aspx  
  
data file referenced directly at:  
http://apps.meckboe.org/pages/Download/VoterDataFile.zip  
  
North Carolina State Board of Elections voter registration and voter history data may be found with the following links:  
https://www.ncsbe.gov/Public-Records-Data-Info/Election-Results-Data#CurrentVoterRegistrationVoterHistoryDatabyCounty  
or  
https://dl.ncsbe.gov/?prefix=data/  

# voting history
https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvhis48.zip
or
http://dl.ncsbe.gov/data/ncvhis48.zip

# voter registration record
https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvoter48.zip
or
http://dl.ncsbe.gov/data/ncvoter48.zip


```{r getStateData, eval=TRUE, echo=TRUE}
temp <- tempfile()
download.file("https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvoter48.zip",temp)
voterRec<- read_tsv(unz(temp, "ncvoter48.txt"))
unlink(temp)

temp <- tempfile()
download.file("https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvhis48.zip",temp)
voterHist<- read_tsv(unz(temp, "ncvhis48.txt"))
unlink(temp)

voterHist1 <- as_tibble(voterHist)

voterHist1 <- voterHist1 %>% mutate(newValue = paste(voting_method, voted_party_cd, voted_party_desc, pct_label, pct_description, ncid, voted_county_id, voted_county_desc, vtd_label, vtd_description, sep = "|"))

voterHist1 <- mutate(voterHist, electionDate = as.Date(election_desc, "%m/%d/%Y"))

voterHist1 <- arrange(voterHist1, electionDate)

#extract duplicated rows for review...edit/rename/combine rows as needed
dups <- voterHist1[duplicated(voterHist1[, 1:4])|duplicated(voterHist1[, 1:4], fromLast=TRUE),]

voterHist1 <- select(voterHist1, -c(4, 7:16))

voterHist2 <- spread(voterHist1, election_desc, newValue, fill = NA, convert = FALSE)
```

```{r getCountyData}
temp <- tempfile()
download.file("http://apps.meckboe.org/pages/Download/VoterDataFile.zip",temp)
voterMeckCo <- read_csv(unz(temp, "voterdatafile.txt"))
voterMeckCo <- read_csv(unz(temp, "voterdatafile.txt"),

#voterMeckCo <- read_csv(unz("C:/Users/Valued User/Documents/CJ Class/FinalProj/VoterDataFile.zip","voterdatafile.txt"),
         col_types = cols(.default = "c", 
                          age = "d", 
                          registr_dt = "?"))
unlink(temp)

# File is very large, so for this assignment I reduced the original population of data down to a random sample of 10,000 records.
set.seed(9)
voterMeckCo <- sample_n(voterMeckCo, 10000)

voterMeckCo <- as_tibble(voterMeckCo)
voterMeckCo <-  voterMeckCo %>% mutate(row = row_number())

# View parsing errors
parseProb <- problems(voterMeckCo)
parseProb <- as_tibble(parseProb)
probRows <- unlist(as.list(distinct(parseProb, row)))

# Filter out rows with parsing errors 
voterMeck <- voterMeckCo %>% filter(!(row %in% probRows))

# Change class of date columns as appropriate:
dateCols1 <- voterMeck[, grepl("date", names(voterMeck))]
dateCols2 <- voterMeck[, grepl("Date", names(voterMeck))]
dates <- c(c(names(dateCols1)), c(names(dateCols2)))

voterMeck[,dates] = apply(voterMeck[,dates], 2, function(x) as.POSIXlt(x, format = "%m/%d/%Y"))

#voterMeck[,dates] = apply(voterMeck[,dates], 2, function(x) as_date(x))

#voterMeck[,dates] = apply(voterMeck[,dates], 2, function(x) as.date(x, format = "%m/%d/%Y"))


# Change class of columns to factors as appropriate:
factCols <- c("precinct_desc", "race_code", "ethnic_code", "sex_code", "res_city_desc", "zip_code", "status_cd", "municipality_desc", "ward_desc", "county_commiss_desc", "school_dist_desc")

#voterMeck[,factCols] = apply(voterMeck[,factCols], 2, function(x) as.factor(x))
voterMeck$precinct_desc <- as.factor(voterMeck$precinct_desc)
voterMeck$race_code <- as.factor(voterMeck$race_code)
voterMeck$ethnic_code <- as.factor(voterMeck$ethnic_code)
voterMeck$sex_code <- as.factor(voterMeck$sex_code)
voterMeck$res_city_desc <- as.factor(voterMeck$res_city_desc)
voterMeck$zip_code <- as.factor(voterMeck$zip_code)
voterMeck$status_cd <- as.factor(voterMeck$status_cd)
voterMeck$municipality_desc <- as.factor(voterMeck$municipality_desc)
voterMeck$ward_desc <- as.factor(voterMeck$ward_desc)
voterMeck$county_commiss_desc <- as.factor(voterMeck$county_commiss_desc)
voterMeck$school_dist_desc <- as.factor(voterMeck$school_dist_desc)

#apply(voterMeck[,factCols], 2, function(x) print(levels(voterMeck[, x])))

............................................
print(levels(voterMeck$race_code))
print(levels(voterMeck$ethnic_code))
print(levels(voterMeck$sex_code))
print(levels(voterMeck$res_city_desc))
print(levels(voterMeck$zip_code))
print(levels(voterMeck$status_cd))
print(levels(voterMeck$municipality_desc))
print(levels(voterMeck$ward_desc))
print(levels(voterMeck$county_commiss_desc))
print(levels(voterMeck$school_dist_desc))
```

selections of various (combinations of?) geographoc, demographic, and other filters.
```{r setFilters, eval=TRUE, echo=TRUE}

```

Can select what election dates to include (All vs. general elections only, vs. non-general elections only). Predictions will be based on filters and date options selected
```{r setDates, eval=TRUE, echo=TRUE}

```

??? coloring for graphs?
```{r setAes, eval=TRUE, echo=TRUE}

```

Summary (e.g., contingency) and raw/subset data tables
```{r allTables, eval=TRUE, echo=TRUE}

```

Plots, graphs and charts. Includes options (as appropriate) for bar/pie & line, percentage/counts, data coloring, limited graph layout/color options
```{r graphs, eval=TRUE, echo=TRUE}

```

visualizations related to data modeling (biplots, other...)
```{r modelviz, eval=TRUE, echo=TRUE}

```

