---
title: "Test Code"
author: "Chinyere Brown"
date: "12/3/2019"
output: html_document
---

```{r setup, eval=TRUE, echo=TRUE}
library(tidyverse)
library(ggplot2)
```

filepath/web address of data. specify data type if not zip. various data manipulation options (reshape and join data, rename/create variables, )  
  
### Websites  
North Carolina State Board of Elections voter registration and voter history data may be found with the following links:  
https://www.ncsbe.gov/Public-Records-Data-Info/Election-Results-Data#CurrentVoterRegistrationVoterHistoryDatabyCounty  
or  
https://dl.ncsbe.gov/?prefix=data/  
```{r getData, eval=TRUE, echo=TRUE}
# voting history
https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvhis48.zip
or

# voter registration record
https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvoter48.zip
or
http://dl.ncsbe.gov/data/ncvoter48.zip


temp <- tempfile()
download.file("https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvoter48.zip",temp)
voterRec<- read_tsv(unz(temp, "ncvoter48.txt"))
unlink(temp)

temp <- tempfile()
download.file("https://s3.amazonaws.com/dl.ncsbe.gov/data/ncvhis48.zip",temp)
voterHist<- read_tsv(unz(temp, "ncvhis48.txt"))
unlink(temp)

voterHist1 <- mutate(voterHist, newValue = paste(voterHist[, 6], voterHist[, 7], voterHist[, 8], voterHist[, 9], voterHist[, 10], voterHist[, 11], voterHist[, 12], voterHist[, 13], voterHist[, 14], voterHist[, 15], sep = "|"))

voterHist1 <- mutate(voterHist, electionDate = as.Date(election_desc, "%m/%d/%Y"))

voterHist1 <- arrange(voterHist1, electionDate)

#extract duplicated rows for review...edit/rename/combine rows as needed
dups <- voterHist1[duplicated(voterHist1[, 1:4])|duplicated(voterHist1[, 1:4], fromLast=TRUE),]


voterHist1 <- select(voterHist1, -c(4, 6:16))

voterHist2 <- spread(voterHist1, election_desc, newValue, fill = NA, convert = FALSE)
```

selections of various (combinations of?) geographoc, demographic, and other filters.
```{r setFilters, eval=TRUE, echo=TRUE}

```

Can select what election dates to include (All vs. general elections only, vs. non-general elections only). Predictions will be based on filters and date options selected
```{r setDates, eval=TRUE, echo=TRUE}

```

??? coloring for graphs?
```{r setAes, eval=TRUE, echo=TRUE}

```

Summary (e.g., contingency) and raw/subset data tables
```{r allTables, eval=TRUE, echo=TRUE}

```

Plots, graphs and charts. Includes options (as appropriate) for bar/pie & line, percentage/counts, data coloring, limited graph layout/color options
```{r graphs, eval=TRUE, echo=TRUE}

```

visualizations related to data modeling (biplots, other...)
```{r modelviz, eval=TRUE, echo=TRUE}

```

